Just algae 18S community comparison

### 2019-11-04 code/community_comparison_18s.Rmd
split up wrangle tasks into scripts, made seperate csvs
path stuff

---
title: "18S Community Comparison"
output: html_notebook
---

```{r libs, results="hide"}
library(tidyverse)
library(here)
library(GUniFrac)
library(vegan)
library(vegalite)
library(fossil)
library(picante)

@@

```{r set}
theme_set(theme_classic())
```

```{r}
path_18s_ra <- here("data/clean/only_algae_18s_rel_abund.csv")
clean_18s_ra <- read_csv(path_18s_ra)

path_tree <- here("intermediate_output/tree/algae_18s/algae_18s_seqs.fasta.treefile")
tree_18s <- read.tree(path_tree)

path_full_18s_tree <- here("intermediate_output/tree/18s/")
full_tree_18s <- read.tree(path_full_18s_tree)

@@

path_field <- here("data/clean/field_clean.csv")
field <- read_csv(path_field)

path_alias <- here("data/sample_aliases.csv")
alias <- read_csv(path_alias)
```

>>>>

---
title: "Just algae 18S community comparison"
output: html_notebook
---

```{r libs, include=F}
library(tidyverse)
library(here)
library(GUniFrac)
library(vegan)
library(vegalite)
library(fossil)
library(picante)

@@

```{r, include=F}
rel_abund <- read_csv(here("data/03_filtered/18s_algae/18s_algae.filtered_cleaned_rel_abund.csv"))
tree_18s <- read.tree(here("output/tree/algae_18s/algae_18s_seqs.fasta.treefile"))

@@

path_field <- here("data/clean/field_clean.csv")
field <- read_csv(path_field)
```
